Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-03-07 manuscript 01/_manuscript/index.qmd
working on table 2

---
title: Does Hemispheric Lateralization Influence Aggressive Treatment in Patients with Intracerebral Hemorrhage?
subtitle: An Analysis of ATACH-2 and ERICH
authors:
  - name: Nikhil Patel
    orcid: 0000-0002-3193-8590
    affiliation: Department of Neurology, Wake Forest University School of Medicine
    roles: data analysis, writing
    corresponding: true
  - name: Matt Jaffa
    affiliation: Department of Neurology, University of Connecticut School of Medicine
  - name: Rahul Karamchandani
    affiliation: Department of Neurology, Wake Forest University School of Medicine
date: last-modified
abstract: |
  Hemispheric laterality blah blah blah
bibliography: references.bib
csl: american-heart-association.csl
mainfont: Figtree

---

```{r}
library(targets)
library(dplyr)
library(targets)
library(withr)
library(here)

@@

@@

## Introduction
The clinical presentation of patients with stroke can vary based on the hemisphere affected, in particular with language, spatial orientation, and emotional processing. Previous research involving patients with ischemic stroke provide evidence that those with right hemispheric injury present later to the hospital and may not be treated as frequently with thrombolytic therapy.[@legge_neglecting_2006; @di_legge_impact_2005-1] On the other hand, there is a hesitation among some practitioners to offer decompressive craniectomy in patients with dominant-hemispheric infarcts. [@lin_decompressive_2021-1]

@@

A total of `r sample_size` patients were included in the analysis.

```{r}

library(gtsummary)

@@

>>>>

---
title: Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention
subtitle: A Bayesian Analysis of ATACH-2 and ERICH
authors:
  - name: Nikhil Patel
    orcid: 0000-0002-3193-8590
    affiliation: Department of Neurology, Wake Forest University School of Medicine
    roles: data analysis, writing
    corresponding: true
  - name: Matt Jaffa
    affiliation: Department of Neurology, University of Connecticut School of Medicine
  - name: Rahul Karamchandani
    affiliation: Department of Neurology, Wake Forest University School of Medicine
  - name: Andrew Asimos
    affiliation: Department of Emergency Medicine, Wake Forest University School of Medicine
  - name: Jonathan Parish
    affiliation: Carolina Neurosurgery & Spine Associates
  - name: Nicholas Allen Morris
    affiliation: Department of Neurology, University of Maryland School of Medicine
date: last-modified
abstract: |
  Hemispheric laterality blah blah blah
bibliography: references.bib
csl: american-heart-association.csl
mainfont: Figtree
---

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 14) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(2)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_line(colour = "#F3F4F5"),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

left_hemisphere_count <- ich_aggressive |>
  filter(ich_laterality == "Left") |>
  count()

@@

## Introduction
The clinical presentation of patients with stroke can vary based on the hemisphere affected, in particular with language, spatial orientation, and emotional processing. Previous research involving patients with ischemic stroke provide evidence that those with right hemispheric injury present later to the hospital and may not be treated as frequently with thrombolytic therapy.[@legge_neglecting_2006; @di_legge_impact_2005] On the other hand, there is a hesitation among some practitioners to offer decompressive craniectomy in patients with dominant-hemispheric infarcts. [@lin_decompressive_2021-1]

@@

### Baseline Characteristics

A total of `r sample_size` patients were included in the analysis, of which `r left_hemisphere_count` (`r left_hemisphere_count/sample_size`) had left hemispheric ICH. They had higher NIHSS scores, higher GCS scores, and lower rates of hypertension as compared to those with right hemispheric ICH (@tbl-1).

```{r table_1}
#| label: tbl-1
#| tbl-cap: "Baseline Characteristics"

@@

### Left hemispheric ICH and neurosurgical intervention

::: {.callout-note}
What am I trying to do here? I want to present the results of the logistic regression showing that after controlling for other factors, there is still a higher probability of a right-hemisphere ICH patient receiving neurosurgical intervention.

I have to change the baseline factor in `ich_laterality` to "Left".

I should report the following: point estimate, 95% CIs, and posterior probability that effect is greater than 0, or for minimal clinically important difference.
:::

```{r neurosurgery}
models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical))
)

table_2 <- with_dir(here(), tar_read(table_2_aggressive))

summary <- modelsummary(models,
  exponentiate = TRUE,
  fmt = fmt_significant(3),
  estimate = "{estimate}",
  statistic = "{conf.low} - {conf.high}",
  coef_omit = "^(?!b_ich_lat)",
  coef_rename = c("b_ich_lateralityRight" = "Right Hemisphere ICH"),
  gof_map = c("none")
)

summary

### Left hemispheric ICH and other measures of aggressive care

### Sensitivity analysis

## Discussion

Hello

### 2024-03-07 manuscript 01/index.qmd
working on table 2

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)

@@

```{r neurosurgery}
models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical))
)

@@

summary

>>>>

```{r}
library(targets)
library(tidyverse)
library(withr)
library(here)
library(scales)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)

@@

```{r neurosurgery}
neurosurgery_mod <- with_dir(here(), tar_read(m_posterior_neurosurgery_canonical))

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical))
)

@@

noquote(summary$"Neurosurgical Intervention"[1])

odds_ratios <- list(
  "Neurosurgical Intervention" = noquote(summary$"Neurosurgical Intervention"[1]),
  "External Ventricular Drain" = noquote(summary$"External Ventricular Drain"[1]),
  "Tracheostomy" = noquote(summary$"Tracheostomy"[1]),
  "Days of Mechanical Ventilation" = noquote(summary$"Days of Mechanical Ventilation"[1]),
  "DNR Order" = noquote(summary$"DNR Order"[1]),
  "Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Withdrawal of Life-Sustaining Therapy"[1]),
  "Early Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Early Withdrawal of Life-Sustaining Therapy"[1])
)

credible_ints <- list(
  "Neurosurgical Intervention" = noquote(summary$"Neurosurgical Intervention"[2]),
  "External Ventricular Drain" = noquote(summary$"External Ventricular Drain"[2]),
  "Tracheostomy" = noquote(summary$"Tracheostomy"[2]),
  "Days of Mechanical Ventilation" = noquote(summary$"Days of Mechanical Ventilation"[2]),
  "DNR Order" = noquote(summary$"DNR Order"[2]),
  "Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Withdrawal of Life-Sustaining Therapy"[2]),
  "Early Withdrawal of Life-Sustaining Therapy" = noquote(summary$"Early Withdrawal of Life-Sustaining Therapy"[2])
)

table_2
